\selectlanguage{english}
% \addcontentsline{toc}{chapter}{Abstract}
\chapter*{Abstract}
One of the major topics in photogrammetry is the automated extraction of
urban objects from data acquired by airborne sensors. What makes this task
challenging is the very heterogeneous appearance of objects like buildings,
streets, trees and cars in very high-resolution data, which leads to high
intra-class variance while the inter-class variance is low. Focus is on
detailed 2D semantic segmentation that assigns labels to multiple object
categories. Further research drivers are very high-resolution data from new
sensors and advanced processing techniques that rely on increasingly mature
machine learning techniques. Despite the enormous efforts spent, these tasks
cannot be considered solved, yet. To my knowledge, no fully automated method
for 2D object recognition is applied in practice today although at least two
decades of research have tried solving this task.


There are many approaches in solving this problem, either machine learning
approach or rule-based algorithm. This thesis focuses on dealing with the
issue as a semantic segmentation perspective. This problem had been being
tackled by applying many supervised machine learning models proposed in
former research works. However, previous models lacked accuracies and
automated transferability when considering different given input data.
Therefore, this thesis comes up with a new problem formulation that can
transfer learnt expertise from basic areas of computer vision in common
sense and fine-tune to adapt for any given data in terms of semantic
segmentation.


Throughout this thesis, a deep learning approach is chosen which two
contemporary classification networks (the VGG net and ResNet), have been
adapted into fully convolutional networks and transfer their learnt
representations by fine-tuning to the segmentation task. With this solution,
not much special domain knowledge is needed to build a high-accuracy model
but only enough relevant data. Practically, my proposed models have achieved
very competitive positions in the 2D Semantic Labelling Contest hosted by
International Society for Photogrammetry and Remote Sensing.
