\addcontentsline{toc}{chapter}{Conclusion}
\chapter*{Conclusion}
This thesis aimed at solving the problem of 2D semantic labelling in aerial
photography by training fully convolutional networks with given labelled data.

\section*{Conclusions}
The following theoretical contents are presented:
\begin{itemize}
    \item Background knowledge about \gls{remote-sensing},
    \gls{aerial-photography} and 2D semantic labelling problem.
    \item Basic insight into machine learning and applications of deep learning
    applied to computer vision.
    \item In-depth discussion about fully convolutional networks to solve
    semantic segmentation problem in computer vision.
\end{itemize}

The thesis has obtained these following practical results:
\begin{itemize}
    \item Successful implementation of 16 proposed \acrshort{fcn} models.
    \item Many hyperparameters and configurations have been tried to select the
    best ones.
    \item The best models can run on both datasets without any significant
    changes.
    \item Achieve better results than prior research.
    \item Achieve very competitive positions in the contest globally.
\end{itemize}

Limitations of the thesis:
\begin{itemize}
    \item Have not achieved the highest positions in both datasets globally yet.
    \item Have not proposed more breakthrough models than any typical
    recognition architectures.
\end{itemize}

\section*{Future Developments}
\begin{itemize}
    \item Do futher research on new models, make better improvements.
    \item Optimise training time, memory and models' complexity.
\end{itemize}
